Understanding the drivers of diurnal and nocturnal urban land surface temperature

### 2019-04-10 report/article.tex
Updates from Overleaf

\begin{figure}[h]
\begin{center}
\includegraphics[width=1.2\linewidth]{fig/map/cities_lst.pdf}
\caption{The land surface temperature in $^o$C of the cities studied.}
\label{fig:cities}
\end{center}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{fig/report/joyplot_lst.png}
    \caption{The distribution of nocturnal and diurnal land surface temperature of the cities studied.}
    \label{fig:joy}
\end{figure}

@@

- include scatter of night vs day LST at 100m - also change the symbols for colorblind - remove background
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/lst_night-vs-day.png}
\caption{The land surface temperature in $^o$C of the cities studied at a 500m square resolution (UPDATE WITH 100m)}
\label{fig:scatter_lst}
\end{center}
\end{figure}
\subsection{Independent variables}
- present correlation matrix of independent variables

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{fig/report/map_nocturnal_lst.pdf}
    \caption{The gridded nocturnal land surface temperature in $^o$C of the cities studied. This is change from the mean (average) for each city.}
    \label{fig:map}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{fig/report/joyplot_lst.pdf}
    \caption{The distribution of nocturnal and diurnal land surface temperature of the cities studied.}
    \label{fig:joy}
\end{figure}

@@

- include scatter of night vs day LST at 100m - also change the symbols for colorblind - remove background
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/lst_night-vs-day_500.pdf}
\caption{The land surface temperature in $^o$C of the cities studied at a 500m square resolution}
\label{fig:scatter_lst}
\end{center}
\end{figure}
\subsection{Independent variables}
- present correlation matrix of independent variables
